---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# coloratio

<!-- badges: start -->
[![Project Status: Concept – Minimal or no implementation has been done
yet, or the repository is only intended to be a limited example, demo,
or
proof-of-concept.](https://www.repostatus.org/badges/latest/concept.svg)](https://www.repostatus.org/#concept)
<!-- badges: end -->

This work-in-progress R package helps calculate color-contrast values so you can make decisions to improve the visual accessibility of text on block-colored backgrounds.

The ultimate aim is to create a tool for compliance with [WCAG 3.0](https://w3c.github.io/silver/guidelines/).

Feel free to add an issue or a make a pull request. Please follow [the code of conduct](#conduct).

## Installation

You can install the development version of {coloratio} from GitHub with:

```{r install, eval=FALSE}
remotes::install_github("matt-dray/coloratio")
```

## Example

### Get contrast ratio

The `cr_get_ratio()` function returns the color-contrast ratio of two user-provided colors. You can provide hex values, named colors, or both.

```{r ratio-example}
library(coloratio)
cr_get_ratio("#000000", "white")
```

You should aim for a value of 4.5 or greater. You'll get a warning if the contrast between the colors is insufficient.

```{r ratio-example-warning}
cr_get_ratio("black", "grey10")
```

[Read more about the calculation](w3.org/TR/WCAG/#dfn-relative-luminance) in the WCAG 2.1 guidance.

### Choose black or white text

You may want to alter programmatically the colour of overlaying text when the underlying colour varies. For example, when putting text over the bars of a grouped bar chart.

The function `cr_choose_bw()` returns `"white"` or `"black"` depending on which has the better contrast ratio with the user-supplied colour.

```{r bw-example-gray}
cr_choose_bw("gray10")
cr_choose_bw("gray90")
```

Black is chosen in the event of a tie and a warning is given.

## Code of Conduct {#conduct}

Please note that the {coloratio} project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
