---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# coloratio

<!-- badges: start -->
[![Project Status: Concept – Minimal or no implementation has been done
yet, or the repository is only intended to be a limited example, demo,
or
proof-of-concept.](https://www.repostatus.org/badges/latest/concept.svg)](https://www.repostatus.org/#concept)
<!-- badges: end -->

This work-in-progress package helps calculate colour-contrast values so you can make decisions to improve the visual accessibility of text on block-coloured backgrounds.

The ultimate aim is to create a tool for compliance with [WCAG 3.0](https://w3c.github.io/silver/guidelines/).

## Installation

You can install the development version of {coloratio} from GitHub with:

```{r install, eval=FALSE}
remotes::install_github("matt-dray/coloratio")
```

## Example

There is currently one function, which assesses the colour-contrast ratio of two user-provided colours. You can provide hex values, named colours, or both.

```{r example}
library(coloratio)
get_ratio("#000000", "white")
```

You should aim for a value of 4.5 or greater. You'll get a warning if the contrast between the colours is insufficient.

```{r example-warning}
get_ratio("black", "grey10")
```

[Read more about the calculation](w3.org/TR/WCAG/#dfn-relative-luminance) in the WCAG 2.1 guidance.
